Using reference models in variable selection \vspace{.1in}

### 2020-07-06 paper/ref_approach.tex
update contributions

\begin{itemize}
\item to show a simple and basic way to frame any variable selection method in the reference model approach,
\item to do a structured comparison for variable selection methods using or not a reference model, both for the the complete and the minimal subset selection,
\item to bring evidence in supporting the projection predictive approach as a principled way to use the reference model.
\end{itemize}

>>>>

\begin{itemize}
\item We show a simple and intuitive way to combine any variable selection method with the reference model approach.
\item We perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection.
\item We provide evidence supporting the projection predictive approach as a principled way to use reference models.
\end{itemize}
